CrypTool Script \\ Mathematics and Cryptography

### 2002-06-28 script/en/chapters/numbertheory.tex
typo

\begin{theorem}\label{thm-zth-ordp}\footnote{Compare the above table with the values for $a^i$ mod 11, with $ 1 \le a,
i < 11$.}$^,$\footnote{Exhausting all possible values of the set is an important cryptographic proposition (compare theorem \ref{thm-zth-exhperm}).}
For a modulus $p$ and $a < p$:
$a^i, i = 1, \cdots, p-1$ assumes all $J(p)$ values $1, \cdots, p-1$ once if and only if $ord_p(a) = J(p)$.
\end{theorem}

>>>>

\begin{theorem}\label{thm-zth-ordp}\footnote{Compare the above table with the values for $a^i$ mod 11, with $ 1 \le a,
i < 11$. Please note that this theorem is not applicable to the above tabel
mod 46.}$^,$\footnote{Exhausting all possible values of the set is an
important cryptographic proposition (compare theorem
\ref{thm-zth-exhperm}). This determines a permutation $\pi(p-1).}
For a modulus $p$ and $a < p$:
$a^i \mbox{mod} p, i = 1, \cdots, p-1$ assumes all $J(p) = p-1$ values $1, \cdots, p-1$ once if and only if $ord_p(a) = J(p)$.
\end{theorem}
